Vertical and oblique transmission with fluctuating transmission

### 2018-03-20 ms/fluctuating_oblique.tex
citation, todo

There has been much less theory developed for fluctuating transmission.
Nevertheless, if we assume that social learning can be affected by weather~\citep{Phithakkitnukoon2012}, food availability, population density, or even political atmosphere, then it is reasonable that the mode and rate of transmission will fluctuate over time. 
For example, it may be the case that during cold seasons offspring are more likely to stay close to their parents and therefore learn vertically, whereas during warm seasons they are more likely to wander and interact with other adults and therefore learn obliquely.

@@

>>>>

There has been much less theory developed for fluctuating transmission.
Nevertheless, if we assume that social learning can be affected by frequency of interactions~\citep{VanSchaik2003}, weather~\citep{Phithakkitnukoon2012}, food availability, population density~\citep{Aureli1997a}, or even political atmosphere, then it is reasonable that the mode and rate of transmission will fluctuate over time. 
For example, it may be the case that during cold seasons offspring are more likely to stay close to their parents and therefore learn vertically, whereas during warm seasons they are more likely to wander and interact with other adults and therefore learn obliquely.

@@

% TODO plot \Delta \rho vs s and show the boundaries
